---
title: 'Assessing the volatility within the South African bond markets, using GARCH
  modelling'
documentclass: elsarticle
Author1: Deborah Kapenda
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
    include:
      in_header: Tex/packages.txt
Email1: deborahkapenda1\@gmail.com
keywords: Multivariate DCC-GARCH \sep South African bonds \sep Volatility \sep Bond
  markets
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage\
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
linenumbers: no
AddTitle: yes
HardSet_layout: yes
bibliography: Tex/ref.bib
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
Ref1: Department of Economics, Stellenbosch University, South Africa
abstract: "This article examines the volatility of the South African bond market. The article illustrates the various methods for measuring volatility by implementing the GARCH and DCC-GARCH models. The article concludes that short- to medium-term SA bonds are more volatile than long-term bonds. Bond yields in developing countries are often higher than those in developed economies. This might be a result of excessive repayment costs, stagnant economic development, and ineffective fiscal and monetary policy execution. In general, bond markets are critical for developing countries because they offer a source of revenue while also allowing the Reserve Bank to exert control over the money supply and consumer demand. Additionally, variables affecting bond market volatility include inflation, currency exchange rates, and economic development. However, modeling the noise is challenging due to the existence of other variables affecting bond yields. The article concludes that the GARCH and DCC-GARCH models are effective in removing noise from volatility presentation. Additionally, the 10-year bond yield exhibits consistency in its returns, corroborating the literature's assertion that short- to medium-term rates are more volatile. Additional study should include a comparison of volatility to that of other developed countries and an analysis of the effect of exchange rate and inflation volatility on bond rates." 
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
knitr::raw_latex("here all your tex content") 
```

```{r include=FALSE}
library(esquisse)
#esquisser(mtcars)
library(dplyr)
library(ggplot2)

# ============== Preamble to load packages ========================== #
if(!require("devtools")){install_github("devtools")}
library(devtools)
# Install pacman to handle installations
install_github("trinker/pacman")
devtools::install_github("KevinKotze/tsm")

# Install the required packages in elagant approach
pacman::p_load(
    "tidyverse",
    "devtools",
    "rugarch",
    "forecast",
    "tbl2xts",
    "lubridate",
    "PerformanceAnalytics",
    "ggthemes",
    "robustbase",
    "tbl2xts",
    "ggplot2",
    "ggthemes",
    "robustbase",
    "fmxdat",
    "extrafont",
    "TTR",
    "naniar",
    "readr",
    "dplyr",
    "tidyr",
    "rmsfuns",
    "naniar",
    "Texevier",
    "reshape2",
    "xts",
    "readr",
    "viridis",
    "viridisLite",
    "rugarch",
    "quantmod",
    "wesanderson",
    "MTS",
    "robustbase",
    "rmgarch",
    "forecast",
    "fGarch",
    "tsm",
    "ccgarch",
    "tseries",
    "xlsx",
    "gdata",
    "readxl",
    "xtable",
    "knitr",
    "xfun")

# ---------------------------------------------Data---------------------------------
SA_bonds <- read_rds("data/SA_Bonds.rds") # SA bond 2 year, 3 month and 10 year
ZA_Infl <- read_rds("data/ZA_Infl.rds") # Inflation in South Africa (High inflation rate, leads to bond holders requiring higher  returns off bonds and thus )
IV <- read_rds("data/IV.rds") # Volatility index
usdzar <- read_rds("data/usdzar.rds") 

library(readxl)
X2yr_bonds <- read_excel("data/2yr_bonds.xlsx", 
    col_types = c("date", "numeric", "numeric", 
        "numeric", "numeric",
        "numeric"))
View(X2yr_bonds)



library(readxl)
X10yr_bonds <- read_excel("data/10yr_bonds.xlsx", 
    col_types = c("date", "numeric", "numeric", 
        "numeric", "numeric",
        "numeric"))
View(X10yr_bonds)

# transformation: reshape to plot
#Change dataset into time series 
xts.SA_bonds <- tbl_xts(SA_bonds)
str(xts.SA_bonds)
head(xts.SA_bonds)
tail(xts.SA_bonds)

xts.2yr <- tbl_xts(X2yr_bonds)
str(xts.2yr)
head(xts.2yr)

xts.10yr <- tbl_xts(X10yr_bonds)
str(xts.10yr)
head(xts.10yr)

xts.IV <- tbl_xts(IV)
xts.ZA_Infl <- tbl_xts(ZA_Infl)

```

```{r include=FALSE}
install.packages("sjPlot", dependencies = T)
```

<!-- ############################## -->

<!-- # Start Writing here: -->

<!-- ############################## -->

# [**Introduction**]{.ul} \label{Introduction}

A government bond is a debt-based investment in which people acquire the
bonds in exchange for a loan from the government. The exchange
represents a guaranteed investment at a predetermined rate of return.
These bonds are used by the government to pay off debt and fund projects
@meyer2020analysis. Numerous factors influence the yield rate. Firstly,
supply and demand in the bond market --- investors want low-risk,
high-return bonds. Secondly, interest rates' movement and level; a high
interest rate above the bond yield results in poor demand for the bond.
Thirdly, credit ratings; although bonds are low-risk investments,
governments may fail, resulting in a credit deterioration. The primary
objective of the South African (SA) bond market is to provide financing
for development projects and debt reduction. Access to global financial
markets, government risk levels, and currency rate volatility all
contribute to the market's development. These variables are heavily
impacted by how the foreign community views the country's economy. It is
critical for the country's bond market to be efficient since it offers
an extra source of revenue and reduces the economy's need for money. In
times of economic expansion, inflation may rise, prompting the central
bank to raise interest rates, resulting in higher bond yields. Investors
want greater yields before investing as a consequence of the pressure
exerted on the bond market by rising inflation rates.

Reasons for the research include the fact that the SA market is
appealing since it serves as a proxy for emerging nations and accounts
for a significant portion of the market. The paper is important because
it looks into the volatility in the South African bond market, which
could help policy-makers stabilize the economy, governance, and politics
to keep the bond market stable. The bond market is critical for funding
debt and infrastructure development; a healthy bond market allows fiscal
and monetary expansion. Therefore the study is significant as literature
has shown a direct relationship between changes in bond market yields
and economic growth. As well as the relationship between bond market
yields, effective governance, and interest rates.

In light of the above, the primary objective of this paper is to analyse
SA's bond market volatility, placing focus on its 3 month, 2 year and 10
year bond yields respectively.

In summarising the main findings of this paper:

-   The data shows a virtual relationship between the SA bond yields,
    the inflation rate, volatility index and the exchange rate. This is
    in line with literature.
-   The period of the 2000s, the aftermath of the dot.com bubble, the
    financial crisis 2007/8 and the 2019 pandemic, contain the highest
    rate of volatility.
-   The GARCH and DCC-GARCH account for the noise in volatility.

The rest of the paper is structured as follows. The data section
provides a description of the dataset used in this paper. Thereafter,
the structure and rationale related to the application of the GARCH and
the DCC-GARCH framework in volatility analysis is discussed throughout
the section Methodology section. The empirical findings from the model
are discussed in the preceding sections, before presenting concluding
remarks.

# [**Data**]{.ul}\label{Data}

The paper uses SA bond market yields, as shown in figure 1, for 1999 to
2021. SA inflation prices are presented in Figure 2. The higher the
inflation rate, results in the increased demand for higher returns. The
pressure placed on the bond market due to an increase in inflation
results in investors demanding higher yields before they invest.
Additionally, the figure depicts that SA bond yields move relative to
inflation. Periods of high inflation prices resulted in a spike in the
bond yields. A consistent inflation price resulted in consistent bond
yields from 2020 until 2019.

The volatility index created by the Chicago Board of Options Exchange
(CBOE) tracks the volatility of S&P 500 Index options (VIX), and the
VXEEM tracks the emerging Markets ETF volatility (Figure 3). The
volatility indices show that they tend to outperform estimates of future
realised volatility and the collection of GARCH volatility models
\@{fernandes2014modeling. The index indicates periods of high volatility
during the global financial crisis and the COVID-19 pandemic. These
periods *correlate* to the performance in the inflation prices (Figure
2) and the bond yields (Figure 1). In other words, the graphs indicate a
movement in a similar pattern.

Lastly, the US and SA exchange rates are shown in Figure 4. Meyer (2020)
explains that the worsening volatility of African countries' exchange
rates has contributed adversely to bond yields. His paper finds that the
exchange rate volatility is one of the limiting factors of the economy's
bond market as it discourages foreign investment into the market
@meyer2020analysis. The figure shows that high/spikes of the exchange
rate in the early 2000s, 2010s and 2019 are similar to that represented
in the volatility index and inflation prices.

```{r yields, fig.align='center', fig.cap="Figure 1 South African bond yields  \\label{yields}", fig.height=3.7, fig.width=7}
asset.names <- colnames(xts.SA_bonds)
plot.xts(xts.SA_bonds, legend.loc = "topright", xlim = "bond yield", grid.col = "white", main = "South Africa's bond yields", ylab = "Bond Yields")
```

```{r inf, fig.align='center', fig.cap="Figure 2 South African inflation prices  \\label{yields}", fig.height=3.7, fig.width=7}
plot.xts(xts.ZA_Infl, legend.loc = "topright", xlim = "bond yield", grid.col = "white", main = "SA inflation prices", ylab = "Inflation rate")
```

```{r iv, fig.align='center', fig.cap="Figure 3 Volatility index  \\label{yields}", fig.height=3.7, fig.width=7}
p1 <- IV %>%
 ggplot() +
 aes(x = date, y = Price, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Time (daily)", y = "Volatility index", subtitle = "Volatility index", caption = "VIX represents volatility index", 
 color = "Index") +
 theme_classic() +
 theme(legend.position = "bottom")

print(p1)
```

```{r uz, fig.align='center', fig.cap="Figure 4 ZAR and USD exchange rate  \\label{uz}", fig.height=3.7, fig.width=7}
ggplot(usdzar) +
  aes(x = date, y = Price, colour = Name) +
  geom_line(size = 0.5) +
  scale_color_viridis_d(option = "viridis", direction = 1) +
  theme_economist_white()
```

### Bond yields

The yield of a bond represents the money lent. The higher the yield, the
higher the return on the investment. Figure 1 shows SA bond yields for
the 3 months, 2 year and 10 year maturity. A significant decline is seen
during 2008 financial crisis as well as during 2020 as caused by the
COVID-19 pandemic. However, one notices a rise in the mid and long term
bonds, while the short term (3M) remains at a constant rate. Usually,
yields with relative maturities move relatively close and may move
together in the same fashion as seen in the diagram.

To compare the performance of SA 2 Year bond yields to that of the US,
UK, Brazil and Nigeria, Figure 5 below shows this. The US and UK bond
market tend to move with each other, while Nigeria's bond yields are
very high. In other words, the mid-term bond rate, the 2-year bond
yield, shows South African yields higher than the United States (US),
United Kingdom (UK) and Brazil. Nigeria has significantly higher yields.
The graph shows that developed countries, the UK and the US, have lower
bond yields than Nigeria, SA, and Brazil. Higher yields in developing
countries may lead to higher costs on loans as the country may have
higher risk ratings.

The graph indicates different volatility processes. A similar pattern is
seen in the 10-year bond yields (Figure 6). The bond spread is seen in
Figure 7, bond spreads show the difference in the 3 month and 2-year
bond yields with the 10-year bond yield as the benchmark. A spread is
used to calculate the value of one bond to another. It is the reflection
of the relative risk of the bonds. Figure 7 indicates rising bond
spreads from 2020, which might mean that bonds are riskier than usual.
One notices that the spread moves in a similar pattern since the terms
are similar (3M and 2Yr) and are affected by the general changes in the
economy.

```{r 2y, fig.align='center', fig.cap="Figure 5 South African bond yields  \\label{2y}", fig.height=3.7, fig.width=7}
#Plot Bond yields of 2-year
asset.names <- colnames(xts.2yr)
plot.xts(xts.2yr, legend.loc = "topleft", xlim = "bond yield", grid.col = "white", main = "2-Year Bond yields", ylab = "Bond Yields")
```

```{r 10y, fig.align='center', fig.cap=" Figure 6 South African bond yields  \\label{10y}", fig.height=3.7, fig.width=7}
#Plot Bond yields of 10-year
asset.names <- colnames(xts.10yr)
plot.xts(xts.10yr, legend.loc = "topleft", xlim = "bond yield", grid.col = "white", main = "10-Year Bond yields", ylab = "Bond Yields")
```

```{r spread, fig.align='center', fig.cap="Figure 7 SA Yield Spreads \\label{spread}", fig.height=3.7, fig.width=7}
ggplot(data = SA_bonds, aes(x = date)) +
  geom_line(aes(y =ZA_10Yr-SA_3M, colour = "SA_3M spread")) +
  geom_line(aes(y =ZA_10Yr-ZA_2Yr, colour = "ZA_2Yr spread")) +
  scale_colour_manual("", 
                      breaks = c("SA_3M spread", "ZA_2Yr spread"),
                      values = c("SA_3M spread"="green", "ZA_2Yr spread"="red")) +
  xlab("Date") +
  scale_y_continuous("Spreads") + 
  labs(title="SA Yield Spreads",
       subtitle = "Yield spreads relative to ZA_10Yr") + theme_economist_white()
```

# [**Methodology**\label{Methodology}]{.ul}

The GARCH model extends the (ARCH) Autoregressive Conditional
Heteroskedasticity model. The GARCH model allows the variance to depend
on its lags and squared residuals. The GARCH model cares for
heteroscedasticity as a variance to be modelled. Heteroscedasticity is
the presence of non-constant variance, which financial time series
contain. The issues that arise when modelling volatility needs to be
done as the most common method, the Ordinary Least Squares (OLS), may
lead to misleading conclusions. Hence, the effectiveness of the GARCH
model is that it accounts for heteroscedasticity, which corrects the
shortcomings of the OLS model. Therefore, GARCH modelling is an
essential element used to model volatility. However, one critic is that
it models conditional variance as a linear function of the squared past
values where a positive shock affects the volatility similarly to an
adverse shock.

Firstly, volatility is investigated where the annualised volatility, the
rolling month estimates and predictive errors are shown. Secondly, the
differentiated yields are calculated and shown graphically, followed by
the autocorrelation results. Thirdly, the Univariate GARCH model is
analysed, followed by the multivariate GARCH model. The Multivariate
DCC-GARCH model is analysed, and the plots for covariance and
correlation are done based on this.

The GARCH: A Generalised Autoregressive Conditional Heteroskedasticity
model is used to handle changing volatility in financial time series
data. The equation below shows the popular GARCH form of the volatility
process @tsay2005analysis. The equation means the current volatility is
equal to the last day's volatility and the last day's return, with
estimated parameters. This type of ARCH class of conditional volatility
models allows heteroscedasticity in the regression. Heteroscedasticity
is when the regression residual is not independent of the predictors.
The DCC-GARCH is the Dynamic Conditional Correlation (DCC) GARCH model,
and the DCC model estimates the correlation matrix directly through the
use of standard residuals.

```{=tex}
\begin{equation}
\sigma^2 = w + \alpha (\epsilon^2_{t-1} )    +    (\beta)  \sigma^2_{t-1}
\label{eq1}
\end{equation}
```
```{=tex}
\begin{equation}
r_{t} = \mu +  \epsilon_{t}
\label{eq2}
\end{equation}
```
```{=tex}
\begin{equation}
\epsilon_{t} = \sigma_{t} . z_{t}
\label{eq3}
\end{equation}
```
```{=tex}
\begin{equation}
\sigma^2 = \alpha + \beta_{1}\epsilon^2_{t-1} + \beta_{t}\sigma^2_{t-1}
\label{eq4}
\end{equation}
```
```{=tex}
\begin{equation}
 z_{t} = N (0,1)
\label{eq5}
\end{equation}
```
# [Analysis and Results]{.ul} \label{cd}

# 1. Volatility \label{Volatility}

## Annualised, rolling volatility and predictive errors

The annualised volatility is calculated as the square root of each yield
and the standard deviation. Figure 8 shows that the annualised
volatility rate and the yields move in a similar pattern. There are
periods of significant fluctuation, followed by periods of low
variation. Figures 9 and 10 represent a visual of the time-variation in
volatility. The assumption made here is that the number of trading days
in a year equals 252 days. The one-month volatility is calculated as the
standard deviation of the last 30 percentage changes in the bond yield
multiplied by the square root of 252. From the figures, one notices that
the standard volatility calculation shows high periods of volatility in
the early 2000s and 2020s. This is later compared to the GARCH
volatility, removing the noise. Figure 10 shows the absolute value of
the prediction errors. The 3 months and 2 Year bond yields show high
predictive errors during the crisis and pandemic.

```{r av, fig.align='center', fig.cap=" Figure 8 Annualised volatility rate  \\label{av}", fig.height=3.7, fig.width=7}
#annualized volatility 
annual_vol <- sqrt(xts.SA_bonds) * sd(xts.SA_bonds)
plot.xts(annual_vol, legend.loc = "topright", ylab = "Annualised volatility rate", grid.col = "white", main = "Annualized Volatility SA bonds")
```

```{r rv1, fig.align='center', fig.cap=" Figure 9 One month rolling volatility  \\label{rv1}", fig.height=3.7, fig.width=7}
# Compute the rolling 1 month estimate of annualized volatility
chart.RollingPerformance(R = xts.SA_bonds, width = 22,
     FUN = "sd.annualized", scale = 252, main = "One month rolling volatility", legend.loc = "topleft") 
```

```{r rv2, fig.align='center', fig.cap="Figure 10 Three month rolling volatility  \\label{rv2}", fig.height=3.7, fig.width=7}
# Compute the rolling 1 month estimate of annualized volatility
chart.RollingPerformance(R = xts.SA_bonds, width = 66,
     FUN = "sd.annualized", scale = 252, main = "Three month rolling volatility", legend.loc = "topleft") 
```

```{r}
#Prediction errors
m <- mean(xts.SA_bonds)
# series of prediction errors
e <- xts.SA_bonds - m
```

```{r pe, fig.align='center', fig.cap="Figure 11 The absolute value of the prediction errors  \\label{pe}", fig.height=3.7, fig.width=7}
par(mfrow = c(1,1), mar = c(3,2,2,2))
plot(abs(e), main = "The absolute value of the prediction errors", legend.loc = "topright", xlim = "bond yield", grid.col = "white" )
```

## Differentiated bond yields and autocorrelation

Calculating the yield levels through "differentiation" allows us to make
the time series independent of time. The calculation is the difference
between the previous yield to the current yield. Figure 12 shows the
yield changes by bond maturity date. One notes negative returns in the
short term bond; much of the volatility clustering is seen in 2-year
bonds during the early 2000s and 2020s. Volatility clustering is the
behaviour of jagged peaks in the series. One notices periods of high and
low volatility in the yield changes. The long term bond has mainly
experienced positive change, and a negative dip is seen in the 2020s;
this may have been due to the pandemic. Furthermore, short and mid-term
are volatile mainly by observing the yield change; the 10-year bond
holds its consistency over time.

Figure 12 shows the yield changes in the bond. The graph shows that the
direction (positive or negative) is independent of the previous day's
returns. The magnitude of the return is similar to the previous day's
return. It shows that the expected return will be similar to a turbulent
tomorrow during a volatile market or crisis. Significant yield changes
tend to happen close to each other. This is known as volatility
clustering.

To show this statistically, one can measure autocorrelation, which shows
how the past depends on the future of a time series. If the
autocorrelation is close to 1, the next day's value is close to today's
value. However, if it is close to 0, the following day's value is
unaffected by today's value. The Autocorrelation figure 13 shows that
each spike that rises above or falls below the dashed lines is
considered to be statistically significant. This means the spike has a
value that is significantly different from zero. If a spike is
significantly different from zero, that is evidence of autocorrelation.
A spike that's close to zero is evidence against autocorrelation. The
figure shows that most of the spikes are not statistically significant.
This indicates that the yields are not highly correlated. The
autocorrelation pattern of the data shows how an observation at time t
is correlated to an observation at time t-k. Figure 13 represents the
autocorrelogram; the blue dashed lines represent numerical limits for
the statistical significance of correlation. The yields show high levels
of autocorrelation for lags up to thirty. Additionally, to investigate
the data further, the Box-Ljung test is conducted. The result rejects no
ARCH effects; therefore, we need to account for the remaining
conditional heteroskedasticity in the series by investigating the GARCH
DCC-GARCH models in the sections that follow.

```{r include = FALSE}
# differentiate the time series 
xts.SA_bonds_diff <- diff.xts(xts.SA_bonds)
#Remove NA variable 
xts.SA_bonds_diff <- xts.SA_bonds_diff[-c(1),]
head(xts.SA_bonds_diff)
```

```{r dt, fig.align='center', fig.cap="Figure 12 South Africa's change in bond yields \\label{dt}", fig.height=5, fig.width=8}
Yield.changes  <- xts.SA_bonds_diff
plot.type1  <- "multiple"
asset.names <- colnames(xts.SA_bonds_diff)
#Plot SA.bonds 
plot.zoo(x = Yield.changes, plot.type = plot.type1, xlab = "Date", col = rainbow(3), main = "South Africa's change in bond yields")  
legend(x = "topright", legend = asset.names, cex = 0.45, lwd = 3, col = rainbow(3))
```

```{r at, fig.align='center', fig.cap="Figure 13 Autocorrelation for 3M, 2Yr, 10Yr bond yield changes respectively  \\label{at}", fig.height=3, fig.width=7}
# Plot the autocorrelations of the yield changes
par(mfrow=c(1,3))
acf_3M <- acf(xts.SA_bonds$SA_3M, na.action = na.pass)
acf_2Yr <- acf(xts.SA_bonds$ZA_2Yr, na.action = na.pass)
acf_10Yr <- acf(xts.SA_bonds$ZA_10Yr, na.action = na.pass)
mtext("Autocorrelation for 3M, 2Yr, 10Yr bond yield changes respectively", side = 3, line = -32, outer = TRUE)
```

# 2. The GARCH model \label{GARCH model}

The above analysis show a presence of volatility clustering, given this,
the GARCH model is presented to capture the expected variance of the
residuals from another model.

## Estimated Volatility and Residuals

Figure 14 - 16 shows the estimated volatility and residuals from the
GARCH model. The figures show periods of high volatility during the
2007- 2009 periods and 2020. The 3 month and 2 year bond yields have
residuals fluctuations whereas the 10 year bond yield is consistent
showing little negative spikes.

```{r v1, fig.align='center', fig.cap=" Figure 14 Estimated volatilities and residuals for ZA_3M  \\label{v1}", fig.height=3.7, fig.width=7}
spec <- ugarchspec(distribution.model = "norm")
fit_3M <- ugarchfit(xts.SA_bonds$SA_3M, spec = spec)
# Save the volatilities and the rescaled residuals
Volatilities_3M <- sigma(fit_3M)
Residuals_3M <- scale(residuals(fit_3M, standardize = TRUE)) * sd(xts.SA_bonds$SA_3M) + mean(xts.SA_bonds$SA_3M)
# Plot the yield changes with the estimated volatilities and residuals
merge_1 <- merge.xts(xts.SA_bonds$SA_3M, Volatilities_3M, Residuals_3M)
plot.xts(merge_1, main = "Estimated volatilities and residuals for ZA_3M", legend.loc = "topright", grid.col = "white", width = 20)
```

```{r v2, fig.align='center', fig.cap="Figure 15 Estimated volatilities and residuals for ZA_2YR  \\label{v2}", fig.height=3.7, fig.width=7}
spec <- ugarchspec(distribution.model = "norm")
fit_2Yr <- ugarchfit(xts.SA_bonds$ZA_2Yr, spec = spec)
# Save the volatilities and the rescaled residuals
volatilities_2Yr <- sigma(fit_2Yr)
residuals_2Yr <- scale(residuals(fit_2Yr, standardize = TRUE)) * sd(xts.SA_bonds$ZA_2Yr) + mean(xts.SA_bonds$ZA_2Yr)
merge_2 <- merge.xts(xts.SA_bonds$SA_3M, volatilities_2Yr, residuals_2Yr)
plot.xts(merge_2, main = "Estimated volatilities and residuals for ZA_2YR", legend.loc = "topright", xlim = "bond yield", grid.col = "white", width = 20 )
```

```{r v3, fig.align='center', fig.cap="Figure 16 Estimated volatilities and residuals for ZA_10YR  \\label{v3}", fig.height=3.7, fig.width=7}
spec <- ugarchspec(distribution.model = "norm")
fit_10Yr <- ugarchfit(xts.SA_bonds$ZA_10Yr, spec = spec)
# Save the volatilities and the rescaled residuals
volatilities_10Yr <- sigma(fit_2Yr)
residuals_10Yr <- scale(residuals(fit_10Yr, standardize = TRUE)) * sd(xts.SA_bonds$ZA_10Yr) + mean(xts.SA_bonds$ZA_10Yr)
# Plot the yield changes with the estimated volatilities and residuals
merge_3 <- merge.xts(xts.SA_bonds$ZA_10Yr, volatilities_10Yr, residuals_10Yr)
plot.xts(merge_3, main = "Estimated volatilities and residuals for ZA_10YR", legend.loc = "topright", xlim = "bond yield", grid.col = "white", width = 20)
```

## GARCH model specification

This is a standard GARCH (1,1); it does an excellent job dealing with
second-order persistence. The weighted ARCH LM test works by regressing
the squared errors on its lags and testing the hypothesis that all
coefficients of the lagged regression are equal to zero. The Weighted
ARCH LM tests show a high p-value. We do not reject the null hypothesis
of no autocorrelation---the lower the p-value, the higher chance of
finding the ARCH effect @perlin2020garch. Figure 13 showed high levels
of autocorrelation. After implementing the GARCH, we have a lower
p-value indicating that we do not reject the null hypothesis. The
results of the GARCH model is found in the Appendix for all bond yield
output.

### 3 Month SA bond yields

```{r}
# Note specify the mean (mu) and variance (sigma) models separately:
garch11 <-  ugarchspec(
    
    variance.model = list(model = c("sGARCH","gjrGARCH","eGARCH","fGARCH","apARCH")[1], 
                          
    garchOrder = c(1, 1)), 
    
    mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    
    distribution.model = c("norm", "snorm", "std", "sstd", "ged", "sged", "nig", "ghyp", "jsu")[1])
```

```{r}
garchfit1 = ugarchfit(spec = garch11, data = xts.SA_bonds$SA_3M) 
```

All coefficients are statistically significant. The mean equation is
positive, implying that the 3-month bond yield is likely to have a
positive return and increase its value in the long run. The sum of
*alpha* and *beta* is 0.9664, less than 1 @perlin2020garch. The high
values of the volatility parameters *alpha* and *beta* may reflect SA's
economy, the high degree of uncertainty and shock propagation.
Conditional Variance plot using GARCH sigma eliminates the unnecessary
noise (Figure 17). The red line is the actual volatility representation.
Figure 18 is a representation of all the GARCH plots.

```{r include=FALSE}
# Model coefficients.
garchfit1@fit$matcoef 
```

```{r echo =  FALSE, results='asis'}
kable(garchfit1@fit$matcoef, caption = "Model coefficients 3 Month")
```

```{r echo =  FALSE, results='asis'}
ic <- infocriteria(garchfit1)
kable(ic, caption = "Information criteria")
```

```{r}
sigma <- sigma(garchfit1) %>% xts_tbl()
colnames(sigma) <- c("date", "sigma")
sigma <- sigma %>% mutate(date = as.Date(date))
```

```{r sg, fig.align='center', fig.cap="Figure 17 Sigma from GARCH 3M Bond  \\label{sg}", fig.height=3.7, fig.width=5}
ggplot(sigma) +
 aes(x = date, y = sigma) +
 geom_line(size = 0.5, colour = "#EF562D") +
 labs(x = "Date", 
 y = "Volatility", title = "Sigma from GARCH 3M Bond") +
 theme_classic()
```

```{r gp1, fig.align='center', fig.cap=" Figure 18 GARCH graph plots ZA_3M \\label{gp1}", fig.height=4, fig.width=10, warning = FALSE, message=FALSE}
par(mar=c(1,1,1,1))
plot(garchfit1, which = "all")
```

### 2 Year SA bond yields

All coefficients are statistically significant. The mean equation is
positive, implying that the 2-year bond yield is likely to have a
positive return and increase its value in the long run. The sum of
*alpha* and *beta* is 0.758, which is less than 1. The high values of
the volatility parameters *alpha* and *beta* may reflect the SA's
economy, the high degree of uncertainty and shock propagation.
Conditional Variance plot using GARCH sigma eliminates the unnecessary
noise (Figure 19); the red line is the actual volatility representation.
Figure 20 is a representation of all the GARCH plots.

```{r}
garchfit2 = ugarchfit(spec = garch11, data = xts.SA_bonds$ZA_2Yr) 
```

```{r include= FALSE}
garchfit2@fit$matcoef # Model coefficients.
```

```{r echo =  FALSE, results='asis'}
kable(garchfit2@fit$matcoef, caption = "Model coefficients 2Year")
```

```{r echo =  FALSE, results='asis'}
ic1 <- infocriteria(garchfit2)
kable(ic1, caption = "Information criteria")
```

```{r}
sigma1 <- sigma(garchfit2) %>% xts_tbl()
colnames(sigma1) <- c("date", "sigma")
sigma1 <- sigma1 %>% mutate(date = as.Date(date))
```

```{r sg1, fig.align='center', fig.cap="Figure 19 Sigma from GARCH 2yr \\label{sg1}", fig.height=3.7, fig.width=5}
ggplot(sigma1) +
 aes(x = date, y = sigma) +
 geom_line(size = 0.5, colour = "#EF562D") +
 labs(x = "Date", 
 y = "Volatility", title = "Sigma from GARCH ZA_2Yr") +
 theme_classic()
```

```{r gp2, fig.align='center', fig.cap="Figure 20 GARCH graph plots ZA_3M \\label{gp2}", fig.height=4, fig.width=10, warning=FALSE, message=FALSE}
par(mar=c(1,1,1,1))
plot(garchfit2, which = "all")
```

### 10 year SA bond yields

All coefficients are statistically significant. The mean equation is
positive, implying that the 10-year bond yield is likely to have a
positive return and increase its value in the long run. The sum of
*alpha* and *beta* is 0.949. This is less than 1. The high values of the
volatility parameters *alpha* and *beta* may reflect the SA's economy,
the high degree of uncertainty and shock propagation. Conditional
Variance plot using GARCH sigma eliminates the unnecessary noise (Figure
21); the red line is the actual volatility representation. Figure 22 is
a representation of all the GARCH plots.

```{r}
garchfit3 = ugarchfit(spec = garch11, data = xts.SA_bonds$ZA_10Yr) 
```

```{r include=FALSE}
garchfit3@fit$matcoef # Model coefficients.
```

```{r echo =  FALSE, results='asis'}
kable(garchfit3@fit$matcoef, caption = "Model coefficients 10Year")
```

```{r echo =  FALSE, results='asis'}
ic2 <- infocriteria(garchfit3)
kable(ic2, caption = "Information criteria")
```

```{r}
sigma2 <- sigma(garchfit3) %>% xts_tbl()
colnames(sigma2) <- c("date", "sigma")
sigma2 <- sigma2 %>% mutate(date = as.Date(date))
```

```{r sg2, fig.align='center', fig.cap="Figure 21 Sigma from GARCH 10Yr \\label{sg2}", fig.height=3.7, fig.width=5}
ggplot(sigma2) +
 aes(x = date, y = sigma) +
 geom_line(size = 0.5, colour = "#EF562D") +
 labs(x = "Date", 
 y = "Volatility", title = "Sigma from GARCH ZA_10Yr") +
 theme_classic()
```

```{r gp3, fig.align='center', fig.cap="Figure 22 GARCH graph plots ZA_10Yr \\label{gp3}", fig.height=4, fig.width=10, warning=FALSE, message=FALSE}
par(mar=c(1,1,1,1))
plot(garchfit3, which = "all")
```

# 3. The DCC-GARCH model \label{DCC-GARCH}

The DCC-GARCH Model is based on the time-varying covariance and
correlation matrices. The above analysis shows the Univariate GARCH
models for each bond. We conduct a DCC-GARCH model to analyse
multivariate to investigate covariance and correlation. The DCC model
specification is a (1,1), then the covariance and correlation matrices
are conducted. This is a three-dimensional object; the twoj ; dimensions
have 3 elements each, and the third has 5715 elements. This means that
5715 of the data is stored in a 3x3 matrix. The correlation and
covariance plots are shown in Figures 23 and 24. The DCC GARCH Fit,
dcca1 and dccb1 tell us how the correlations evolve autoregressively.
dcca1 provides the contribution of the realised correlation matrix from
the last period, while dccb1 contributes to a long-run correlation
matrix that is due to all previous periods. The output shows that dccb1
is significant.DCC fit output are found in the appendix. The forecast
shows no correlation between the bond yields expect for the 3 month and
10-year bond showing a slight correlation. The covariance between the 10
year and 2 year bond is forecasted to be high.

```{r}
#estimate these univariate GARCH models using AR(1) GARCH(1,1) model and replicate the model 3 times because we have 3 year to maturity bonds. 
uspec.n <- multispec(replicate(3, garch11))
```

```{r}
#Estimate the univariate GARCH models using multifit command 
multf <- multifit(uspec.n, xts.SA_bonds)
```

```{r}
#This models the univariate volatilities as per uspec.n and the complex dynamic structure of the correlation matrix of dccorder c(1,1)
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), distribution = 'mvnorm')
```

```{r}
fit1 <-  dccfit(spec1, data = xts.SA_bonds, fit.control = list(eval.se =TRUE), fit = multf)
```

```{r include=FALSE}
covariance1 <- rcov(fit1)
dim(covariance1)
correlation1 <- rcor(fit1)
dim(correlation1)
```

```{r cov1, echo =  FALSE, results='asis', include= FALSE}
covariance1[,,dim(covariance1)[3]]
kable(ic2, caption = "Covariance matrix")
```

```{r cov2,  echo =  FALSE, results='asis', include= FALSE}
correlation1[,,dim(correlation1)[3]]
kable(ic2, caption = "Correlation matrix")
```

```{r cc1, fig.align='center', fig.cap="Figure 23 Correlation\\label{cc1}", fig.height=4, fig.width=7}
par(mfrow=c(3,1))  # this creates a frame with 3 windows to be filled by plots
plot(as.xts(correlation1[1,2,]),main="SA_3M and ZA_10Yr")
plot(as.xts(correlation1[1,3,]),main="SA_3M and ZA_2Yr")
plot(as.xts(correlation1[2,3,]),main="ZA_10Yr and ZA_2Yr")
```

```{r cc2, fig.align='center', fig.cap="Figure 24 Covariance \\label{cc2}", fig.height=4, fig.width=7}

par(mfrow=c(3,1))  # this creates a frame with 3 windows to be filled by plots
plot(as.xts(covariance1[1,2,]),main="SA_3M and ZA_10Yr")
plot(as.xts(covariance1[1,3,]),main="SA_3M and ZA_2Yr")
plot(as.xts(covariance1[2,3,]),main="ZA_10Yr and ZA_2Yr")
```

### DCC Forecast

```{r}
#Use the estimated model to produce forecast for the covariance or correlation matrix
dccf1 <- dccforecast(fit1, n.ahead = 10)
```

```{r cc3, fig.align='center', fig.cap="Figure 25 DCC Series Unconditional Forecast \\label{cc3}", fig.height=5, fig.width=7}
plot(dccf1, which=1, main = "DCC")
```

```{r cc4, fig.align='center', fig.cap="Figure 26 DCC Sigma Unconditional Forecast \\label{cc4}", fig.height=5, fig.width=7}
plot(dccf1, which=2, size = 400, ax.lab = 1.9, 
     cex.axes = 1, cex.main = 0.05, cex.sub = 2)
```

```{r cc5, fig.align='center', fig.cap="Figure 27 DCC Unconditional Covariance Forecast \\label{cc5}", fig.height=4, fig.width=10}
plot(dccf1, which=3, cex.main = 0.05)
```

```{r cc6, fig.align='center', fig.cap="Figure 28 EW Forecast Portfolio with Unconditional limits \\label{cc6}", fig.height=4, fig.width=10}
plot(dccf1, which= 5, main = "DCC ")
```

```{r cc9, fig.align='center', fig.cap="Figure 31 DCC Conditional Covariance \\label{cc9}", fig.height=3.7, fig.width=8}
plot(fit1, which=3, series=c(1,2))
```

### Correlation and covariance forecast

```{r}
Rf <- dccf1@mforecast$R
Hf <- dccf1@mforecast$H
Qf <- dccf1@mforecast$Q
Rbarf <- dccf1@mforecast$Rbar
muf <- dccf1@mforecast$mu
```

```{r}
corf_310 <- Rf[[1]][1,2,]  # Correlation forecasts between SA_3M and ZA_10Yr
corf_32 <- Rf[[1]][1,3,]  # Correlation forecasts between SA_3M and ZA_2Yr
corf_102 <- Rf[[1]][2,3,]  # Correlation forecasts between ZA_10Yr and ZA_2Yr
```

```{r}
covf_310 <- Hf[[1]][1,2,]  # covariance forecasts between SA_3M and ZA_10Yr
covf_32 <- Hf[[1]][1,3,]  # covariance forecasts between SA_3M and ZA_2Yr
covf_102 <- Hf[[1]][2,3,]  # covariance forecasts between ZA_10Yr and ZA_2Yr
```

```{r cc7, fig.align='center', fig.cap="Figure 29 Sigma from GARCH 10Yr \\label{cc7}", fig.height=6, fig.width=7}
par(mfrow=c(3,1))  # this creates a frame with 3 windows to be filled by plots
c_310 <- c(tail(correlation1[1,2,],20),rep(NA,10))  # gets the last 20 correlation observations
cf_310 <- c(rep(NA,20),corf_310) # gets the 10 forecasts
plot(c_310,type = "l",main="Correlation SA_3M and ZA_10Yr")
lines(cf_310,type = "l", col = "blue")

c_32 <- c(tail(correlation1[1,3,],20),rep(NA,10))  # gets the last 20 correlation observations
cf_32 <- c(rep(NA,20),corf_32) # gets the 10 forecasts
plot(c_32,type = "l",main="Correlation SA_3M and ZA_2Yr")
lines(cf_32,type = "l", col = "blue")

c_102 <- c(tail(correlation1[2,3,],20),rep(NA,10))  # gets the last 20 correlation observations
cf_102 <- c(rep(NA,20),corf_102) # gets the 10 forecasts
plot(c_102,type = "l",main="Correlation ZA_10Yr and ZA_2Yr")
lines(cf_102,type = "l", col = "blue")
```

```{r cc8, fig.align='center', fig.cap="Figure 30 Sigma from GARCH 10Yr \\label{cc8}", fig.height=6, fig.width=7}
par(mfrow=c(3,1))  # this creates a frame with 3 windows to be filled by plots
c_310 <- c(tail(covariance1[1,2,],20),rep(NA,10))  # gets the last 20 correlation observations
cv_310 <- c(rep(NA,20),covf_310) # gets the 10 forecasts
plot(c_310,type = "l",main="Covariance SA_3M and ZA_10Yr")
lines(cv_310,type = "l", col = "blue")

c_32 <- c(tail(covariance1[1,3,],20),rep(NA,10))  # gets the last 20 correlation observations
cv_32 <- c(rep(NA,20),covf_32) # gets the 10 forecasts
plot(c_32,type = "l",main="Covariance SA_3M and ZA_2Yr")
lines(cv_32,type = "l", col = "blue")

c_102 <- c(tail(covariance1[2,3,],20),rep(NA,10))  # gets the last 20 correlation observations
cv_102 <- c(rep(NA,20),covf_102) # gets the 10 forecasts
plot(c_102,type = "l",main="Covariance ZA_10Yr and ZA_2Yr")
lines(cv_102,type = "l", col = "blue")
```

# [**Conclusion**]{.ul} \label{Conclusion}

This paper offers a perspective on volatility modelling for the SA bond
market. Furthermore, this research focused on modelling volatility using
the GARCH and DCC-GARCH models. The main findings uncovered in the paper
suggest that bond yields tend to cluster during high volatile periods.
These periods include the financial crisis and COVID-19; yields during
volatile periods face a higher dependence on the previous yields. The
GARCH and DCC-GARCH models smoother volatilities over time.

As such the bond market is significant for two reasons: it offers an
extra income source and impacts consumer purchasing power. First, bond
market volatility increases investor risk and affects SA's sovereign
debt markets and portfolio management. Second, a turbulent economy has a
detrimental effect on the bond market, reducing the government's
capacity to service its debt. The paper's weakness is that it does not
directly compare South Africa's volatility to other developed countries.
Additional research may be conducted to model the volatilities in the US
and the UK to establish an appropriate comparison. However, the figures
indicate that developed country bond rates move similarly, although
developing country bond yields tend to be higher. Therefore, further
prediction and forecasting of the bond markets is necessary.

\newpage

# [**Appendix**]{.ul}\label{Appendix}

```{r}
garchfit1 = ugarchfit(spec = garch11, data = xts.SA_bonds$SA_3M) 
garchfit1
```

```{r}
garchfit2 = ugarchfit(spec = garch11, data = xts.SA_bonds$SA_3M) 
garchfit2
```

```{r}
garchfit3 = ugarchfit(spec = garch11, data = xts.SA_bonds$SA_3M) 
garchfit3
```

```{r}
#Estimate the univariate GARCH models using multifit command 
multf <- multifit(uspec.n, xts.SA_bonds)
multf
```

```{r}
fit1 <-  dccfit(spec1, data = xts.SA_bonds, fit.control = list(eval.se =TRUE), fit = multf)
fit1
```

```{r}
#Use the estimated model to produce forecates for the covariance or correlation matrix
dccf1 <- dccforecast(fit1, n.ahead = 10)
dccf1
```

\newpage

<!-- Make title of bibliography here: -->

<!-- \newpage -->

# [**References**]{.ul} \label{References}
